---
title: "Block jackknife joint GWAS enrichment test"
author: "Alexandru Ioan Voda"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Block jackknife joint test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installing the package and downloading the dependencies

For the final function of these lines, accept the download and installation of MAGMA and LDSC (and their model weights and data dependencies):

```{r eval=FALSE}
if (!require("gwascelltyper", quietly = TRUE))
    devtools::install_github("alexandruioanvoda/gwascelltyper")

# once installed:
library("gwascelltyper")
download_dependencies(population = "eur")
```

## Running the block jackknife test

To just load some pre-processed block jackknife data and run the final test on them, we can now just do the following:
```{r eval=FALSE}
download.file(url = "https://s3.tebi.io/bjk-vignette/bjk_vignette.tgz",
              destfile = "bjk_vignette.tgz")
utils::untar("bjk_vignette.tgz") # This unzips into a folder called "To_share".

library("gwascelltyper")
mat <- readRDS("./To_share/bjk_last_step_data.rds")
head(mat)
finalStep_bjk_joint_test(mat)
```

Here, we can see that the P-value for dendritic cells (DC) tested with Crohn's disease GWAS sumstats is much more confident (Z=6.97) in the block jackknife joint test than in MAGMA (Z=5.6) or LDSC (Z=4.8) alone.

## Running it from A to Z?

To get a matrix like `mat`, we can run the `compute_bjk_enrichment_discrete()` function, which also computes the above `bjk` Z-score as well, by default.

```{r eval=FALSE}
library("gwascelltyper")
gene_sets <- readRDS("./To_share/geneset.rds")[c("DC", "All_genes_control")]
# We're subsetting to just one gene-set (DC -> dendritic cells)
# and the control (background) gene-set.

results <- compute_bjk_enrichment_discrete(gene_sets = gene_sets,
                                sumstats_files = c("./To_share/magma_CD.gwas", "./To_share/ldsc_CD.gwas.gz"),
                                output_dir = "./To_share/interm", # where we'll store our intermediary files.
                                pop = "eur",
                                n_blocks = 200,
                                number_of_threads = 1) # On macbooks, this can be increased to 2 or 3 to increase the computation speed

results[[2]] # The matrix with delete-n values
results[[1]] # The final bjk, magma and ldsc values
```

This function can take a lot of time to run, and creates a lot of dependency files. Make sure you have a few free gigabytes of storage.

