---
title: "Test enrichment in two genesets"
author: "Alexandru Ioan Voda"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Test enrichment in two genesets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Downloading example GWAS summary statistics

First, navigate in R to whichever folder you want to run this analysis in (e.g. where you'd like temporary data to be downloaded in).

This snippet will download and decompress an archive containing GWAS summary statistics for Crohn's disease in our current directory:
```{r eval=FALSE}
print("hi")

```

## Formatting it for MAGMA

To preview how a correct & minimal summary statistics file would look like for MAGMA, run:
```{r eval=TRUE}
library(gwascelltyper)
munge_sumstats_for_MAGMA(preview=TRUE)
```

Now, let's attempt to get them formatted for our analysis:
```{r eval=FALSE}
library(gwascelltyper)

path = paste0(getwd(), "/cd_build37_40266.txt") # it could also be "/path/to/your/GWASsumstats.txt"

munge_sumstats_for_MAGMA(sumstats_raw = path)

file.exists(paste0(path, "_processed.sumstats"))
```
